---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# AIriskjobs

<!-- badges: start -->

<!-- badges: end -->

The goal of AIriskjobs is designed to analyze and visualize job market trends affected by advancements in artificial intelligence. This package aims to provide users with the tools to identify at-risk job categories, assess the potential impact of AI on employment, and generate insights to inform workforce planning and policy decisions. By simplifying the data analysis process, AIriskjobs enables users to harness the power of AI data to understand labor market dynamics effectively.

## Installation

You can install the development version of AIriskjobs from [GitHub](https://github.com/) with:



## Example

This is a basic example which shows you how to solve a common problem:

```{r example}


```


