---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# AIriskjobs

<!-- badges: start -->

<!-- badges: end -->

The goal of AIriskjobs is designed to analyze and visualize job market trends affected by advancements in artificial intelligence. This package aims to provide users with the tools to identify at-risk job categories, assess the potential impact of AI on employment, and generate insights to inform workforce planning and policy decisions. By simplifying the data analysis process, AIriskjobs enables users to harness the power of AI data to understand labor market dynamics effectively.

## Installation

You can install the development version of AIriskjobs from [GitHub](https://github.com/) with:

```{r}
# Install remotes if not already installed
#if (!requireNamespace("remotes", quietly = TRUE)) {
#  install.packages("remotes")
#}

# Install AIriskjobs package from GitHub
#remotes::install_github("ETC5523-2024/assignment-4-packages-and-shiny-apps-Vaishhh125")

```


## Shiny App

AIriskjobs includes a Shiny application to allow interactive exploration of the job market data. You can launch the app with the following command:

```{r}
#library(AIriskjobs)
#run_app()  # Launches the 'jobsatrisk' Shiny app
```

## Vignettes

For an in-depth walkthrough and additional examples, check out our vignette by running the following command in R:

```{r}
#vignette("AIriskjobs_overview", package = "AIriskjobs")
```

## License

This package is licensed under the MIT License. See LICENSE for details.

