---
title: "AIriskjobs Overview"
author: "Vaishnavi Amuda"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{AIriskjobs Overview}
  %\VignetteKeywords{AI jobs analysis}
  %\VignettePackage{AIriskjobs}
---

```{r setup, include=FALSE}
# Set CRAN mirror
options(repos = c(CRAN = "https://cran.rstudio.com/"))

```

# Introduction
This vignette provides an overview of the **AIriskjobs** package, including how to use its functions and the Shiny app.

## Installation
To install the **AIriskjobs** package from GitHub, use the following command:

```{r, eval=FALSE}
# Install devtools if you haven't already
install.packages("devtools")

# Install AIriskjobs
devtools::install_github("ETC5523-2024/assignment-4-packages-and-shiny-apps-Vaishhh125")
```

# Launching the Shiny App

To launch the Shiny app that comes with the package, run:

```{r, eval=FALSE}
library(AIriskjobs)
run_app()  
```

# Analyzing Job Data

You can analyze job data by calculating the average salary based on the level of AI adoption in the industry. Here’s how you can summarize the data:

#### Example usage

```{r}
# Load the dataset
library(AIriskjobs)
data("AIriskjobs")

# Calculate average salary by AI adoption level
avg_salary_by_adoption <- aggregate(Salary_USD ~ AI_Adoption_Level, data = AIriskjobs, FUN = mean)

# Display the average salary by AI adoption level
print(avg_salary_by_adoption)

```


# Conclusion

This vignette highlights the key features of the AIriskjobs package. For more information on specific functions, refer to the package documentation.














